Identification of high-yielding soybean lines with exceptional seed composition qualities

### 2022-04-11 doc/manuscript/manuscript.Rmd
small changes to the yield summary table, and utility function file

## Statistical Analysis
The data for seed yield, seed oil, and seed protein contents were analyzed using a mixed model with the metan[@r_metan] R package. Environment, replication nested with environment, and the interaction of genotype with environment were considered to be random effects while genotype was considered to be a fixed effect.

>>>>

## Statistical Analysis
The data for seed yield, seed oil, and seed protein contents were analyzed using a mixed model with the metan[@olivotoMetanPackageMultienvironment2020] R package. Environment, replication nested with environment, and the interaction of genotype with environment were considered to be random effects while genotype was considered to be a fixed effect.
